---
title: "Lab 07 - Modelling course evaluations"
author: "Izzat Maulana"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
evals %>% 
  ggplot(aes(x = score)) +
  geom_histogram()

evals %>% 
  summarise(median_s = median(score),
            mean_s   = mean(score),
            range_s  = max(score) - min(score))
```

*Add your other details and narratives here.*
Using the visualization, the distribution has a negative skew, with the median score being 4.3 and the mean being 4.17. This implies that, on average, the sample population would rate their classes as very good (4). This is as expected as students would be able to choose their own classes, allowing them to pick classes that they are interested at, which would result in higher satisfaction. 

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
evals %>% 
  ggplot(aes(x = bty_avg, y = score)) + 
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

evals %>% 
  ggplot(aes(x = bty_avg, y = score)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE)

resid <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(bty_avg ~ score, data =evals)

bty_avg_score_fit_aug <- augment(resid$fit)

ggplot(bty_avg_score_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted score", y = "Residuals")
```

*Add your narrative and other details here.*
There's a weak relationship between bty_avg and score. geom_jitter() allows to visualise overlapping data points, so the first visualisation appeared as if there's a less plots.  

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(bty_avg ~ score, data = evals)
```

```{r tidy-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

*Add your linear model here. Don't worry too much about notation, you can use things like score-hat.*

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit,eval=FALSE}
evals %>% 
  ggplot(aes(x = bty_avg, y = score)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE)
  
```

3. Interpret the slope of the linear model in context of the data.
For every increase of bty_avg by 1, the score of the class is expected to be higher, on average, by 0.526 score. 

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.
At the bty_avg of 0, the score is estimated to be at 2.22. This intercept makes sense in this context as, there may be professores who received a bty score of 0. 

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)$r.squared
```

*Add your interpretation here*
Has a $r^2$ of 0.035, implying that there is no correlation. 

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic, eva; = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(score_bty_aug) + ...
```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
# ... 
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

*Add your narrative here. Use in-line code!*

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

```{r eval = FALSE}
ggplot(___) + ...
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
